SDR enhancement by clouds

### 2024-03-06 article/article.Rmd
Commit 2024-03-06 13:09

@@

@@

>>>>

## Clear Sky Irradiance

In order to set a threshold for the CE we had to create an approximation of "clear sky" radiation for the whole period.
For this reason, we decided to use the Libradtran....cite..... model with monthly climatological data from AERONET, as our site is part of this network and operates a Cimel photometer since 2003.
We also use the Sun's total solar irradiance from NOAA ....cite..... and Earth - Sun distance calculated by Astropy....cite......
We simulated the solar radiation on $0.2^\circ$ SZA's step, for AOD at $500\,\text{nm}$ and offsets of $\pm1$ and $\pm2\sigma$, for water column $\pm1$ and $\pm2\sigma$, and for two atmospheric profiles "AFGL atmospheric constituent profile, midlatitude summer (afglms)" and "AFGL atmospheric constituent profile, midlatitude winter (afglmw)"....cite...... .

- Kurudz wavelength
- solver

After some evaluation of the modelled conditions, in relation to the GHI data, we choose as more representative of the clear sky radiation, the case with $t_{500} - 1\sigma$ and $wc - 1\sigma$.

Lookup table creation ......

@@

To select the exact values of the threshold used (Equation \ref{eq:CE4}), we implemented manual inspection of the CE indemnification, on specially selected days from the whole dataset. 
We used seven sets of random selected days, with characteristics relevant to the efficiency of the threshold.

six criteria in order to evaluate random multiples of 25 days with some characteristics

- 20 days with the largest over irradiance CE events
- 30 days with largest total over irradiance
- 20 days without clouds (CSid)
- days without clouds and EC events
- days with    clouds and EC events
- random days
- manual selected days

@@

## Other method used and rejected
